Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-05 paper.tex
more on scheduling

            Scientific workflows typically rely on HPC schedulers for 
            distributed scheduling on clusters. These schedulers include SLURM,
            PBS,TORQUE, SGE, HTCondor and Mesos. Additionally, they may provide
            their own form of scheduling for computations on a single node. 
            Nipype uses mutliproc... etc. BigData frameworks, such as Dask,
            also provide interfaces to these HPC schedulers. However, other
            frameworks such as MapReduce and Spark are limited to BigData 
            clusters such as Yet Another Resource Negotiator (YARN and MESOS).
            Spark additionally provides its own standalone scheduler. Similarly
            to scientific workflows, all three BigData frameworks provide their
            own schedulers for single-node scheduling.

            Spark's standalone scheduler is a simple scheduler that can be used
            in distributed workflows. It can execute in two modes: client and
            cluster. In client mode, the  \note{cannot run in cluster mode in pyspark}

            YARN needs hadoop cluster

            Mesos can run on HPC

            dask distributed
            \note{scientific: SLURM, PBS, SGE, HTCondor, Mesos (sometimes)
            big data: mapreduce - local or YARN, Spark - standalone, YARN or 
            Mesos, dask: any (easy to extend to any scheduler)}
        \section{Performance enhancement strategies}\label{other}
            scientific: workflow checkpointing (looking at file hashes)
            big data: data locality, in memory computing, lazy evaluation

>>>>

            Scientific workflows typically rely on HPC schedulers for 
            distributed scheduling on clusters. These schedulers include SLURM,
            PBS,TORQUE, SGE, HTCondor and Mesos. Additionally, they may provide
            their own form of scheduling for computations on a single node. 
            BigData frameworks, such as Dask,
            also provide interfaces to these HPC schedulers. However, other
            frameworks such as MapReduce and Spark are limited to BigData 
            clusters such as Yet Another Resource Negotiator (YARN and MESOS).
            Spark additionally provides its own standalone scheduler. Similarly
            to scientific workflows, all three BigData frameworks provide their
            own schedulers for single-node scheduling.

            Spark's standalone scheduler is a simple scheduler packaged with 
            Spark that can be used in distributed workflows. It can be used
            for single-node and cluster deployments. For cluster deployments,
            Spark has two execution modes: client and cluster. For client 
            execution, the application driver is intended to be executed on the
            client node. In cluster mode, however, the driver is intended to be
            running on a compute node. Cluster mode can ensure fault-tolerance 
            of not only the workers and master, but also the driver. However,
            cluster mode is not available to PySpark deployments using the 
            standalone scheduler.

            YARN is the main scheduler used for MapReduce applications. It was 
            designed in order to decouple resource management from the 
            MapReduce programming model while also addressing issues created 
            by ad-hoc clusters, such as Hadoop on Demand (HoD), and helped 
            users transition to shared Hadoop clusters. YARN is not restricted 
            to MapReduce applications, and can also be used as a scheduler for 
            Spark and Dask applications. Unlike Spark's standalone scheduler, 
            YARN cluster deployment mode can be used with PySpark.

            Mesos is another scheduler compatible with Hadoop and Spark 
            applications. It differs with YARN in that it is designed for the
            efficient resource sharing of many cluster computing frameworks,
            not just those that belong to the Hadoop family. Cluster deployment
            mode is also available to PySpark applications using Mesos.

            Dask provides support for two built-in schedulers: single machine
            and distributed. The single machine scheduler is Dask's default
            scheduler. It allows users to parallelize their application on a
            single machine at either the thread or process level. For any 
            application that needs to scale to multiple nodes, the Dask 
            distributed scheduler is recommended. Dask distributed can also be
            run on a single machine as is useful to use in applications with 
            significant data transfers as it employs more efficient 
            locality-aware scheduling strategies.

            Unlike Spark, Dask can interface with HPC schedulers. The 
            dask-jobqueue interface is compatible with PBS, SLURM and SGE 
            resource managers, while the dask-drmaa interface is compatible 
            with any DRMAA compliant resource manager. It is recommended to use
            these interfaces for interactive scheduling, but they can also be
            used for batch processing.

            Since Spark does not natively interface with HPC schedulers, 
            the use of overlay Spark clusters, similar to HoD, has been 
            investigated for Spark applications running on HPC. The reasons 
            listed for HoD's failure include poor 
            data locality when deploying a dynamic cluster on a shared HDFS 
            instance, inability to resize cluster resulting in idle nodes and 
            high cluster allocation latency. To address the issue of high 
            cluster allocation, pilot-agent scheduling strategies can be used.
            Pilot-agent scheduling strategies allow for clusters to grow 
            dynamically and to add nodes when required. This relieves users, 
            in the case of Spark, from having to wait until all nodes become 
            available to begin execution. Both papers \note{jha and baer} use 
            this strategy. Furthermore, pilot-agent scheduling could be adapted
            to enable smart cluster resizing. Conversly, maintaining data 
            locality using a shared HDFS instance will remain an issue.

        \section{Performance enhancement strategies}\label{other}
            scientific: workflow checkpointing (looking at file hashes)
